\addcontentsline{toc}{chapter}{References}
\begin{thebibliography}{99}
\bibitem{EWKTheory1} S. L. Glashow, Nucl. Phys. 22, 579 (1961).
 \bibitem{EWKTheory2} S. Weinberg, Phys. Rev. Lett. 19, 1264 (1967).
January 2, 2009 14:52 WSPC - Proceedings 
\bibitem{EWKTheory3} A. Salam In Elementary Particle Theory, ed. N. Svartholm (Almquist and
Wiksells, Stockholm 1969), 367-377.
\bibitem{Langacker:2009my} P.~Langacker, ``Introduction to the Standard Model and Electroweak Physics,'' arXiv:0901.0241 [hep-ph].
\bibitem{Goldstone} J. Goldstone, A. Salam and S. Weinberg, Phys. Rev. 127, 965 (1962).
\bibitem{Gargamelle} F J Hasert et al. 1973a Phys. Lett. 46B 121.
\bibitem{UA1} G. Arnison et al., Phys. Lett. B166, p. 484 (1986).
\bibitem{UA2} R. Ansari et al., Phys. Lett. B186, p. 440 (1987).
\bibitem{Altarelli} New Physics and the LHC. Guido Altarelli, (Rome III U. \& INFN, Rome3 \& CERN) . RM3-TH-08-9, CERN-PH-TH-2008-085, May 2008. 35pp. 
\bibitem{LEPHiggsLimit} The LEP Electroweak Working Group, http://lepewwg.web.cern.ch/LEPEWWG/
\bibitem{HiggsTeV} T. Aaltonen et al. (CDF and D0 Collaborations), Phys. Rev. Lett. 104, 061802 (2010).
\bibitem{ExtraDim} For a review and a list of references, see, for example, J. Hewett and M.
Spiropulu, Ann.Rev.Nucl.Part.Sci. 52, 397 (2002), hep-ph/0205196.
\bibitem{TOPPAS} CMS Collaboration, ``Selection of Top-Like Events in the Dilepton and Lepton-plus-Jets Channels in Early 7 TeV Data'', CMS-PAS-TOP-10-004. 
\bibitem{SUSYPAS} CMS Collaboration, ``Performance of Methods for Data-Driven Background Estimation in SUSY Searches'', CMS-PAS-SUS-10-001. 
\bibitem{ATLASHIGGS} ATLAS Collaboration, Expected performance of the ATLAS experiment: detector, trigger, physics, CERN Report, CERN-OPEN-2008-020, arXiv:0901.0512
\bibitem{CMSPhysics} CMS Collaboration, CMS Physics Technical Design Report, Vol II: Physics Performance, CERN/LHCC/2006-021 (2006), J. Phys. G Nucl. Part. Phys. 34 (2006) 995.
\bibitem{ATLASPhysics} ATLAS Collaboration, Expected performance of the ATLAS experiment: detector, trigger, physics, CERN Report, CERN-OPEN-2008-020, arXiv:0901.0512.
\bibitem{D0}  DØ Collaboration, V.M. Abazov, et al., Fermilab-PUB-09-326-E, Phys. Rev.
Lett., arXiv:0906.4819, submitted for publication.
\bibitem{SUSY} S.P. Martin, hep-ph/9709356 (1997).
\bibitem{GUT} Georgi, H.; Glashow, S.L. (1974). "Unity of All Elementary Particle Forces". Physical Review Letters 32: 438-441. doi:10.1103/PhysRevLett.32.438
\bibitem{HERA }P. Nadolsky, D. R. Stump, and C. P. Yuan. Semi-inclusive hadron production at hera: The effect of QCD gluon resummation. Phys. Rev., D61:014003, 2000.
\bibitem{AltarelliParisi} G. Altarelli, G. Parisi, and R. Petronzio. Transverse momentum in drell-yan processes.
Phys. Lett., B76:351, 1978.
\bibitem{PYTHIA} T. Sjostrand, S. Mrenna, and P. Skands. Pythia 6.4 physics and manual. JHEP, 05:026, 2006.
\bibitem{Herwig} G. Marchesini et al. Herwig: A monte carlo event generator for simulating hadron emission reactions with interfering gluons. version 5.1 - april 1991. Comput. Phys. Commun.,
67:465{508, 1992}.
\bibitem{MC@NLO} S. Frixione and B. R. Webber. The mc@nlo event generator. 2002.
\bibitem{ResBos} G. A. Ladinsky and C. P. Yuan. The nonperturbative regime in qcd resummation for gauge boson production at hadron colliders. Phys. Rev., D50:4239, 1994.
\bibitem{Css} F. Landry, R. Brock, G. Ladinsky, and C. P. Yuan. New fits for the non-perturbative parameters in the css resummation formalism. Phys. Rev., D63:013004, 2001.
\bibitem{POWHEG} Nason, JHEP 0411:040,2004.



\bibitem{CMSDetTDR} {\it{CMS Physics. Technical Design Report (vol. 1: Detector Performance and Software)}},  CMS collaboration, CERN-LHCC-2006-01.
\bibitem{LHCMachine}  {\it{LHC Machine}}, Lyndon Evans and Philip Bryant (editors) 2008 JINST 3 S08001
\bibitem{LHCDesign}	 O.S. Br\''uning et al. (eds.), The LHC design report v.1: the LHC Main Ring,CERN-2004-003-V-1, http://cdsweb.cern.ch/record/782076; The LHC design report v.2 : theLHC Infrastructure and General Services, CERN-2004-003-V-2,http://cdsweb.cern.ch/record/815187; M. Benedikt et al. (eds.), The LHC design report v.3 :the LHC Injector Chain, CERN-2004-003-V-3, http://cdsweb.cern.ch/record/823808.
\bibitem{Tevatron} http://www.fnal.gov/
\bibitem{ATLAS} ATLAS Collaboration, ATLAS: technical proposal for a general-purpose pp experiment atthe Large Hadron Collider at CERN, CERN-LHCC-94-43,http://cdsweb.cern.ch/record/290968.
\bibitem{CMS}CMS collaboration, CMS technical proposal, CERN-LHCC-94-38,http://cdsweb.cern.ch/record/290969.
\bibitem{LHCb}LHCb collaboration, LHCb technical proposal, CERN-LHCC-98-004,http://cdsweb.cern.ch/record/622031.
\bibitem{TOTEM} TOTEM collaboration, W. Kienzle et al, TOTEM, Total cross section, elastic scattering anddiffractive dissociation at the LHC: Technical Proposal, CERN-LHCC-99-007,http://cdsweb.cern.ch/record/385483.
\bibitem{ALICE} ALICE collaboration, ALICE: Technical proposal for a Large Ion collider Experiment at theCERN LHC, CERN-LHCC-95-71, http://cdsweb.cern.ch/record/293391
\bibitem{lumiStudy} THE LHC STUDY GROUP, Design study of the large hadron collider (LHC): a multiparticlecollider in the LEP tunnel, CERN-91-03, http://cdsweb.cern.ch/record/220493
\bibitem{magnet} P. Fabbricatore et al., The construction of the modules composing the CMS superconducting coil, IEEE Trans. Appl. Supercond. 14 (2004) 552.
\bibitem{tracker1} CMS collaboration, The CMS tracker system project: technical design report, CERN-LHCC-98-006, http://cdsweb.cern.ch/record/368412.
\bibitem{tracker2} CMS collaboration, The CMS tracker: addendum to the technical design report, CERN-LHCC-2000-016, http://cdsweb.cern.ch/record/490194.
\bibitem{CMSTDR} CMS collaboration, CMS Physics Technical Design Report Volume 1: Detector
Performance and Software, CERN-LHCC-2006-001, http://cdsweb.cern.ch/record/922757;
CMS collaboration, CMS Physics Technical Design Report Volume 2: Physics
Performance, J. Phys. G 34 (2006) 995, CERN-LHCC-2006-021,
http://cdsweb.cern.ch/record/942733.
\bibitem{Castor}A. Panagiotou et al., CASTOR engineering design report, CMS Note (2008).
\bibitem{MuonTDR} CMS collaboration, The CMS muon project, technical design report,
CERN-LHCC-97-032, http://cdsweb.cern.ch/record/343814.
\bibitem{CSC} G. Charpak and F. Sauli, High-accuracy, two-dimensional read-out in multiwire
proportional chambers, Nucl. Instrum. Meth. 113 (1973) 381.
\bibitem{RPC} R. Santonico and R. Cardarelli, Development of resistive plate counters, Nucl. Instrum.
Meth. 187 (1981) 377.
\bibitem{Computing} CMS collaboration, CMS: The computing project. Technical design report, CERN-LHCC-2005-023.
\bibitem{HLT} CMS COLLABORATION group, W. Adam et al., The CMS high level trigger, Eur. Phys. J.
C 46 (2005) 605 [hep-ex/0512077].
\bibitem{KalmanFilter} P. Billoir, R. FrÄuwirth and M. Regler, Nucl Instr. Meth. A241 (1985) 115.
\bibitem{CMSDATAWorkflow}  CMS data processing workflows during an extended cosmic ray run, CMS Collaboration 2010 JINST 5 T03006, doi: 10.1088/1748-0221/5/03/T03006. 
\bibitem{CMSDAQ} P. Sphicas ed., CMS: The TriDAS project. Technical design report, Vol. 2: Data acquisition and high-level trigger, CERN-LHCC-2002-026.
\bibitem{WLCG} Worldwide LHC Computing Grid (WLCG), http://lcg.web.cern.ch/LCG/public/default.htm.
\bibitem{ROOT} R. Brun and F. Rademakers, ROOT: an object oriented data analysis framework, Nucl. Instrum. Meth. A 389 (1997) 81; see also http://root.cern.ch.
\bibitem{ORACLE} Kevin Loney, Oracle Database 11g The Complete Reference,
   Oracle, Release 1 (11.1),  2008.
 \bibitem {POOLORA} Z.Xie et al., POOL Persistency Framework for the LHC: New Developments and CMS Applications { \em  Proc. of ``Frontier Science 2005: New Frontiers in Sub nuclear Physics}, 12--17 September, 2005 Milan, Italy''.
  \bibitem{INB} C. Janot, "L'ASSURANCE DE LA QUALITE POUR UNE INSTALLATION NUCLEAIRE DE BASE (AQ-INB)".
 \bibitem{PVSS}  M. Gonzalez-Berges, The Joint Controls Project Framework, {\em Proceeding of the International Conference on Computing in High Energy Physics (CHEP 2003)}, 24--28 March 2003, La Jolla, California.
\bibitem{FRONTIER} B.Blumenfeld et al., CMS conditions data access using FroNTier, {\em 2008 J. Phys.: Conf. Ser. 119 072007}.
\bibitem{CondCHEP09} G.Govi et al., CMS Offline Conditions Framework and Services, {\em International Conference on Computing in High-Energy Physics Conference (CHEP 2009), Distributed Processing and Analysis track}, 23--27 March 2009, Prague, Czech Republic.

\bibitem{POOL} D.Dullman et al.,  THE LCG POOL Project - General Overview and Project Structure, {\em Proc. CHEP 2003 MOKToo7, La Jolla, March 24-28 2003}.
\bibitem {PopCon}  M.De Gruttola et al.  First experience in operating the population of the condition databases of the CMS experiment, {\em International Conference on Computing in High-Energy Physics Conference (CHEP 2009), Distributed Processing and Analysis track}, 23--27 March 2009, Prague, Czech Republic.
\bibitem{JINSTPersistent} M.De Gruttola et al., \emph{Persistent storage of non-event data in the CMS databases}, JINST 5:P04003,2010.
\bibitem{CMSSW} C.D. Jones et al., Analysis environments for CMS, {\em J. Phys.: Conf. 2008 Ser. 119 032027 }.
\bibitem{EDM} C.D. Jones et al., The New CMS Event Data Model and Framework, {\em Procedings of the International Conference on Computing in High-Energy Physics (CHEP 2006)}, 13--17 February 2006, T.I.F.R. Mumbai, India.
\bibitem{SQLite} http://www.sqlite.org/
\bibitem{PopConMonitoring} Ignas Butenas et al., PopCon monitoring: web application for detailed real-time database transaction monitoring, {\em Proceedings of the 15th International Conference on Distributed Multimedia Systems}, 10--12 September 2009, San Francisco Bay, USA. 
\bibitem{JSON}  Crockford, Douglas (May 28, 2009). "Introducing JSON". http://json.org. Retrieved July 3, 2009.
\bibitem{CRAB} D. Spiga et al., The CMS Remote Analysis Builder (CRAB), Lect. Notes Comput. Sci. 4873 (2007)
580.
\bibitem{CMScosmicRays} CMS Collaboration, ``Performance of CMS muon reconstruction in cosmic-ray events'', JINST 5 (2010) T03022. doi:10.1088/1748-0221/5/03/T03022.
\bibitem{PASMuon} CMS Collaboration, ``Performance of muon identification in pp collisions at $\sqrt{s}$ = 7 TeV'', CMS PAS MUO-10-002 (2010).
\bibitem{LEP} Precision electroweak measurements on the z resonance. Phys. Rept., 427:257, 2006.
\bibitem{ICHEP2010} http://www.ichep2010.fr/.
\bibitem{GEANT} GEANT4 Collaboration, S. Agostinelli et al., GEANT4: A simulation
toolkit, Nucl. Instrum. Meth. A506 (2003) 250303.
\bibitem{CMSLumi} CMS Collaboration, ``Measurement of CMS luminosity'', CMS PAS EWK-2010-004 (2010).
\bibitem{PASEWK} CMS Collaboration, ``Measurements of Inclusive W and Z Cross Sections in pp Collisions at $\sqrt{7}$  TeV'', CMS PAS EWK-2010-002 (2010).
\bibitem{ClopperPearson} Clopper, C.; Pearson, E. S. (1934). "The use of confidence or fiducial limits illustrated in the case of the binomial". Biometrika 26: 404-413.
\bibitem{PLR} S. Baker and R. Cousins, Clarification of the Use
of Chi-Square and Likelihood Functions in Fits to Histograms, NIM
221:437 (1984)
\bibitem{MCFM} J. Campbell and R.K. Ellis, Monte Carlo for FeMtobarn processes,
1449 http://mcfm.fnal.gov/.
\bibitem{AN_2010_264}  CMS Collaboration, ``Updated Measurements ofInclusiveW and Z Cross Sections at 7 TeV'', CMS AN-2010-264
\bibitem{PerugiaLumi}  ``Luminosity measurements at LHC''. S. de Capua, (CERN) , F. Ferro, (INFN, Genoa) , M. De Gruttola, (INFN, Naples) , M. Villa, (INFN, Bologna) . 2008. 12pp.
Prepared for 5th Italian Workshop on LHC Physics (In Italian), Perugia, Italy, 30 Jan - 2 Feb 2008.
Published in Nuovo Cim.123B:423-434,2008. 
\end{thebibliography}